\documentclass[sigconf]{acmart}

% Remove this for camera-ready
\settopmatter{printacmref=false} % Removes citation information below abstract
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
\settopmatter{printfolios=true}

\usepackage{times}
\usepackage[utf8]{inputenc}
\usepackage{url}
\usepackage{array,multirow}
\usepackage{xspace}
\usepackage{xcolor}
\usepackage{color, colortbl} 
\usepackage{balance}
\usepackage{paralist}
\usepackage{cleveref}
%\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{pifont}
\usepackage{array}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{bm}
\usepackage{enumitem}
\setlength {\marginparwidth}{2cm}
\usepackage{todonotes}
\usepackage{arydshln}
\usepackage{makecell}
\usepackage{tabularx}
\usepackage{authblk}
\usepackage{caption}
\usepackage{soul,color}
%\usepackage{subcaption}
\usepackage{mwe}
\usepackage{ifthen}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{epsfig}
\usepackage[tight,footnotesize]{subfigure}

\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

\input{macros}
\begin{document}

\title{Topic-based service discovery for the Ethereum P2P network}
\author{}


\begin{abstract}
Peer-to-Peer (P2P) Networks  are being increasingly deployed in distributed systems. They are being used in blockchains (Ethereum, Bitcoin), storage systems (IPFS, Stor4j) and more. One of the main functionality of P2P network is the ability to collectively keep information in the form of a key-value store. However, the current implementations either trade security for efficiency (structured P2P networks) or vice-versa (unstructured P2P networks). 

In this work, we propose \sysname - a P2P key/value store implementation which enables secure, efficient and robust information storage and retrieval. Our system can be deployed on any Distributed Hash Table (DHT). \sysname stores data on multiple nodes for increased security that can be later found within abounded amount of time guaranteeing high efficiency. We implement a robust admission mechanism limiting the resource usage by its participants and preventing a vast range of malicious behaviours. 

We present the design of \sysname and evaluate the system in multiple scenarios. Compared to the state-of-the-art, our system achieves high security, more equal load distribution, lower computational and communication overhead and better robustness in the presence of a powerful attacker.

%The Ethereum blockchain runs a Peer-to-Peer (P2P) network that rely on Kademlia Distributed Hash Table (DHT) for peer discovery and exchanging pending transactions and mined blocks. 
%Apart from supporting blockchain data exchange, the Ethereum P2P network is used by other applications taking advantage of the existing infrastructure to facilitate bootstraping of their own, application-specific networks. However, in order to achieve this task, peers using the same application must first find each other among other, unrelated nodes.

%In this work, we propose a service discovery system (\sysname) which enables secure and robust discovery of application-specific peers in a large, host P2P network. 
%Our system enables nodes to associate themselves with a set of \emph{topics}. The association is collectively stored by the network, and can be later found by interested peers within a bounded amount of time. \sysname included a robust admission mechanism limiting the resource usage by its participants and preventing a vast range of malicious behaviours. 

%We present the design of \sysname and evaluate the system in multiple scenarios. Compared to the state-of-the-art, our system achieves more equal load distribution, lower computational and communication overhead and better robustness in the presence of a powerful attacker.
\end{abstract}

\maketitle
%\input{sections/new_introduction}
\input{sections/intro-bullets}

%\input{sections/background}
\input{sections/background_high_level}

\input{sections/model}

\input{sections/challenges}

\input{sections/new_overview}

\input{sections/placement}

\input{sections/registration}

%\input{sections/recap}
\input{sections/waiting}

\input{sections/evaluation}

\input{sections/related}

\input{sections/conclusions}

%\input{sections/notes}

\clearpage
% ========= references =========
\bibliographystyle{plain}
\bibliography{references}

\end{document}
