%%% where comments go to die but continue to haunt the living


\er{General comments (20220914) after NDSS reject:
\begin{enumerate}
	\item We need to clarify the difference, if any, between \sysname and discv5. Ideally we will want to update the online description which is already several months, if not years, old. I would advocate to present \sysname as the central component of discv5, and detail what are the helping protocols around it (unless, of course, my understanding is incorrect).
	\item Need experiments on prototype.
	\item The use of 100 IPs for the Sybils did not convince one of the two reviewers. Not sure how to fix this?
	\item We should make sure the disctinction between the Ethereum blockchain and the Ethereum ecosystem is clear (confusion with second reviewer).
\end{enumerate}
}
\mk{
Responses to the comments above:
\begin{enumerate}
    \item We consulted it with Felix, at agreed that we can call our think Discv5, while calling the previous one \discv. We should just explain that both Discv5 and \discv have other components (e.g., slightly different encrypted communication) that we don't consider here.
    \item In progress
    \item We'll increase this value in the testbed experiments - it shouldn't influence us that much. 
    \item Yeah, I thought the first part of the introduction was enough, but apparently it wasn't. 
\end{enumerate}
}

%\input{sections/new_introduction}

% \er{Suggestions for alternative titles:
% \begin{itemize}
%   \item \sysname: Robust and efficient topic discovery in the Ethereum ecosystem
%   \item \sysname: Robust and efficient topic discovery in Ethereum 2.0
%   \item \sysname: Scalable and resilient topic membership management in Ethereum 2.0
%   \item \sysname: A robust and scalable topic discovery protocol for the next Ethereum generation
%   \item Resilient topic discovery in Ethereum with \sysname
%   \item Scalable and resilient topic discovery in Ethereum with \sysname
%   \item \sysname: Efficient, decentralized topic discovery for the Ethereum P2P network
%   \item \sysname: Robust and efficient decentralized membership management for applications of the Ethereum ecosystem
% \end{itemize}
% }